### 2022-06-23 pv_evaluation/templates/inventor/2-summary.qmd
Refactor (#10)
* update

* add sphinx doc

* update

* add html docs

* add module docs

* update

* update; not enough memory

* add callout tips
Tweaks (#22)
* update record sampling analysis

* update docs; fix bug with cluster_precision_recall

* update

* refactor estimators

* refactor estimators

* refactor estimators

* update

* update

* update

```{python}
summarizers = {filename: InventorDisambiguationSummary(filename, processed_data_dir=".") for filename in {{ summary_table_files }} }
```

@@

```{python}
compare_plots(*[s.plot_cluster_size_distribution() for s in summarizers.values()])
```

@@

```{python}
compare_plots(*[s.plot_entropy_curve() for s in summarizers.values()])
```

@@

```{python}
compare_plots(*[s.plot_cluster_unique_name_distribution() for s in summarizers.values()])
```

@@

```{python}
compare_plots(*[s.plot_homonymy_rate_distribution() for s in summarizers.values()])
```

>>>>

```{python}
summarizers = {filename: InventorDisambiguationSummary(filename) for filename in {{ summary_table_files }} }
```

@@

:::{.column-body-outset}
```{python}
fig = compare_plots(*[s.plot_cluster_size_distribution() for s in summarizers.values()])
fig.update_layout(autosize=False, width=800)
fig.show()
```
:::

@@

:::{.column-body-outset}
```{python}
fig = compare_plots(*[s.plot_entropy_curve() for s in summarizers.values()])
fig.update_layout(autosize=False, width=800)
fig.show()
```
:::

@@

:::{.column-body-outset}
```{python}
fig = compare_plots(*[s.plot_cluster_unique_name_distribution() for s in summarizers.values()])
fig.update_layout(autosize=False, width=800)
fig.show()
```
:::

@@

:::{.column-body-outset}
```{python}
fig = compare_plots(*[s.plot_homonymy_rate_distribution() for s in summarizers.values()])
fig.update_layout(autosize=False, width=800)
fig.show()
```
:::
